---
title: "Descriptive Analysis"
output: html_notebook
---

This notebook shows descriptive statistics of the results obtained with the decompilers. 

# Load required packages

```{r}
library(tidyverse)
library(VennDiagram)
theme_set(theme_bw())

# Set up a different colour palette
# library(RColorBrewer)
# ggplot <- function(...)
#     ggplot2::ggplot(...) + 
#   scale_color_discrete(palette = "Spectral") +
#   scale_color_brewer(palette = "Spectral") + 
#   scale_fill_brewer(palette = "Spectral")
```

# Read the dataset

```{r}
dataset <- read.csv("data/dataset.csv")
```

# General summary of the dataset

```{r}
summary(dataset)

# summary of numeric variables
dataset %>%
  filter(!is.na(distanceToOriginal) &
           !is.na(nbNodesOriginal) & nbNodesOriginal != 0) %>%
  dplyr::select(Decompiler, distanceToOriginal, nbNodesOriginal) %>%
  group_by(Decompiler) %>%
  summarise(
    min = min(distanceToOriginal / nbNodesOriginal),
    q25 = quantile(distanceToOriginal / nbNodesOriginal, 0.25),
    median = median(distanceToOriginal / nbNodesOriginal),
    q75 = quantile(distanceToOriginal / nbNodesOriginal, 0.75),
    max = max(distanceToOriginal / nbNodesOriginal),
    mean = mean(distanceToOriginal / nbNodesOriginal),
    sd = sd(distanceToOriginal / nbNodesOriginal)
  )

# summary of non-numeric variables
dataset$isRecompilable <- as.factor(dataset$isRecompilable)
dataset$passTests <- as.factor(dataset$passTests)

dataset %>%
  dplyr::select(Decompiler, isRecompilable, passTests) %>%
  group_by(Decompiler) %>%
  dplyr::count(isRecompilable, passTests)
```

# Which is the best decompiler?

### Semantically admisible vs. semantically correct

```{r}
dataset %>%
  dplyr::select(Project,
                Decompiler,
                ClassCompiler,
                passTests,
                bytecodeDistance) %>%
  filter(passTests == F & bytecodeDistance == 0)
```


### Distribution of distance to original

```{r}
# Function used to plot the means 
fun_mean <- function(x) {
  return(data.frame(
    y = round(mean(x), digits = 2),
    label = round(mean(x, na.rm =
                         T), digits = 2)
  ))
}

# Distance to the original
dataset %>%
  filter(!is.na(distanceToOriginal) &
           !is.na(nbNodesOriginal) & nbNodesOriginal != 0) %>%
  ggplot(aes(Decompiler, distanceToOriginal / nbNodesOriginal)) +
  geom_violin(outlier.alpha = 0.2, fill = "#619CFF") +
  geom_boxplot(width = .1, outlier.colour = NA) +
  # add the means
  stat_summary(
    fun.y = mean,
    geom = "point",
    shape = 18,
    colour = "black",
    size = 4,
    position = position_dodge(width = 0.75)
  ) +
  stat_summary(
    fun.y = mean,
    geom = "point",
    shape = 18,
    colour = "#00BA38",
    size = 3,
    position = position_dodge(width = 0.75)
  ) +
  stat_summary(
    fun.data = fun_mean,
    geom = "text",
    vjust = -0.5,
    size = 3.5,
    position = position_dodge(width = 0.75)
  ) +
  scale_y_continuous(limits = c(0, 0.5)) +
  theme(legend.position = "none") +
  coord_flip()

ggsave(filename = "figures/distances.pdf", device="pdf", height = 4, width = 6,  units = c("in"))
```

### Distribution of recompilable and testable types per decompilers

```{r}
# Distribution of Recompilable Classes for each Decompiler
dataset %>% 
  dplyr::select(Decompiler, isRecompilable) %>% 
  group_by(Decompiler) %>% 
  count(Recompilable = isRecompilable) %>% 
  ggplot(aes(Decompiler, n)) +
  geom_bar(aes(fill = Recompilable), position = "dodge", stat="identity") +
  ylab("Classes") +
  ggtitle("Distribution of Recompilable Classes for each Decompiler") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave(filename = "figures/recompilable_decompilers.pdf", device="pdf", height = 4, width = 6,  units = c("in"))

# Distribution of tests results for each Decompiler
dataset %>%
  dplyr::select(Decompiler, passTests) %>%
  filter(!is.na(passTests)) %>%
  group_by(Decompiler) %>%
  count(PassTests = passTests) %>%
  ggplot(aes(Decompiler, n)) +
  geom_bar(aes(fill = PassTests), position = "dodge", stat = "identity") +
  ylab("Tests") +
  ggtitle("Distribution of Tests Results for each Decompiler") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave(filename = "figures/testable_decompilers.pdf", device="pdf", height = 4, width = 6,  units = c("in"))

# Distribution of tests results for each Compiler
dataset %>%
  filter(Project != "commons-lang" & passTests == TRUE) %>%
  dplyr::select(Decompiler, Compiler, passTests) %>%
  filter(!is.na(passTests)) %>%
  group_by(Decompiler, Compiler) %>%
  count(PassTests = passTests) %>%
  ggplot(aes(Decompiler, n, fill = Compiler)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = n),
            position = position_dodge(width = 0.9),
            vjust = -0.3) +
  ylim(0, 1000) +
  ylab("Tests") +
  scale_fill_manual(values = c("#F8766D", "#619CFF")) +
  # ggtitle("Distribution of Tests Results for each Compiler") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.position = "top")

ggsave(filename = "figures/testable_compilers.pdf", device="pdf", height = 4, width = 6,  units = c("in"))

# javac
javac <- dataset %>%
  filter(Compiler == "javac" &
           isRecompilable == TRUE & passTests == FALSE) %>%
  mutate(DecClass = paste(as.character(Class), as.character(Decompiler), sep = "&")) %>%
  dplyr::select(Class, Decompiler, Compiler, passTests, DecClass) %>%
  dplyr::select(DecClass)

# ecj
ecj <- dataset %>%
  filter(Compiler == "ecj" &
           isRecompilable == TRUE & passTests == FALSE) %>%
  mutate(DecClass = paste(as.character(Class), as.character(Decompiler), sep = "&")) %>%
  dplyr::select(Class, Decompiler, Compiler, passTests, DecClass) %>%
  dplyr::select(DecClass)

# Split string by & using regular expression
javac_only <- setdiff(javac, ecj) %>%
  mutate(
    Class = str_extract(DecClass, "[^&]+"),
    Decompiler = str_extract(DecClass, "[^&]+$"),
    Compiler = "javac"
  ) %>%
  select(Class, Compiler, Decompiler) %>%
  group_by(Decompiler, Compiler) %>%
  summarise(n = n())

ecj_only <- setdiff(ecj, javac) %>%
  mutate(
    Class = str_extract(DecClass, "[^&]+"),
    Decompiler = str_extract(DecClass, "[^&]+$"),
    Compiler = "ecj"
  ) %>%
  select(Class, Compiler, Decompiler) %>%
  group_by(Decompiler, Compiler) %>%
  summarise(n = n())

both <- dplyr::intersect(javac, ecj) %>%
  mutate(
    Class = str_extract(DecClass, "[^&]+"),
    Decompiler = str_extract(DecClass, "[^&]+$"),
    Compiler = "both"
  ) %>%
  select(Class, Compiler, Decompiler) %>%
  group_by(Decompiler, Compiler) %>%
  summarise(n = n())

separated <- rbind(javac_only, ecj_only)

bind_rows(separated, both) %>%
  ggplot(aes(Decompiler, n, fill = Compiler)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = n),
            position = position_dodge(width = 0.9),
            vjust = -0.3) +
  ylab("# Classes") +
  ylim(0, 62) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.position = "top")

ggsave(filename = "figures/r_not_t_compilers.pdf", device="pdf", height = 4, width = 6,  units = c("in"))
```

### Distribution of recompilable and testable types per projects

```{r}
# Distribution of Recompilable Classes for each Project
dataset %>%
  dplyr::select(Project, Decompiler, isRecompilable) %>%
  group_by(Project, Decompiler) %>%
  count(Decompilable = isRecompilable) %>%
  ggplot(aes(Decompiler, n)) +
  geom_bar(aes(fill = Project), position = "dodge", stat = "identity") +
  ylab("# Classes") +
  ggtitle("Distribution of Recompilation of Classes for each Project") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_grid(Decompilable ~ .)
  
ggsave(filename = "figures/recompilable_projects.pdf", device="pdf", height = 5, width = 8,  units = c("in"))

# Distribution of Testable Classes for each Project
dataset %>%
  dplyr::select(Project, Decompiler, passTests) %>%
  filter(!is.na(passTests)) %>% 
  group_by(Project, Decompiler) %>%
  count(Testable = passTests) %>%
  ggplot(aes(Decompiler, n)) +
  geom_bar(aes(fill = Project), position = "dodge", stat = "identity") +
  ylab("# Classes") +
  ggtitle("Distribution of Tests Results for each Project") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_grid(Testable ~ .)
  
ggsave(filename = "figures/testable_projects.pdf", device="pdf", height = 5, width = 8,  units = c("in"))
```

### Distribution of recompilable and testable ratios per projects

```{r}
# Distribution of Recompilable Classes for each Project
dataset %>%
  dplyr::select(Project, Decompiler, isRecompilable) %>%
  group_by(Project, Decompiler) %>%
  count(Decompilable = isRecompilable) %>%
  mutate(true_ratio = n / sum(n)) %>%
  ggplot(aes(Decompiler, true_ratio)) +
  geom_bar(aes(fill = Project), position = "dodge", stat = "identity") +
  ylab("Ratio") +
  ggtitle("Distribution of Recompilation Frequencies of each Project") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_grid(Decompilable ~ .)
  
ggsave(filename = "figures/recompilable_projects_ratios.pdf", device="pdf", height = 5, width = 8,  units = c("in"))

# Distribution of Testable Classes for each Project
dataset %>%
  dplyr::select(Project, Decompiler, passTests) %>%
  filter(!is.na(passTests)) %>% 
  group_by(Project, Decompiler) %>%
  count(Testable = passTests) %>%
  mutate(true_ratio = n / sum(n)) %>%
  ggplot(aes(Decompiler, true_ratio)) +
  geom_bar(aes(fill = Project), position = "dodge", stat = "identity") +
  ylab("Ratio") +
  ggtitle("Distribution of Tests Results Frequencies for each Project") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_grid(Testable ~ .)
  
ggsave(filename = "figures/testable_projects_ratios.pdf", device="pdf", height = 5, width = 8,  units = c("in"))
```

### Decompilers that produce recompilable types which do not pass the tests (false positives)

```{r}
dataset %>%
  filter(isRecompilable == TRUE & passTests == FALSE) %>% 
  count(Decompiler, Project) %>% 
  ggplot(aes(x = reorder(Decompiler, -n), y = n, fill = Project)) +
  geom_col() +
  xlab("Decompiler") +
  ylab("# Classes") +
  ggtitle("Projects Producing Recompilable Classes Which do not Pass the Tests") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

ggsave(filename = "figures/projects_recompilable_types_fail_tests.pdf", device="pdf", height = 5, width = 8,  units = c("in"))

# Plot Categories of Outputs for Each Decompiler
dataset %>%
  dplyr::select(Decompiler, Project, isRecompilable, passTests) %>%
  filter(is.na(passTests) == FALSE) %>%
  mutate(Category = ifelse(
    isRecompilable == FALSE,
    "NOT R",
    ifelse(
      isRecompilable == TRUE & passTests == FALSE,
      "R AND NOT P",
      ifelse(isRecompilable == TRUE & passTests == TRUE,
             "R AND P",
             "NA")
    )
  )) %>%
  group_by(Decompiler, Project) %>%
  count(Categories = Category) %>%
  ggplot(aes(x = reorder(Decompiler, -n), y = n)) +
  geom_bar(aes(fill = Project), position = "stack", stat = "identity") +
  stat_summary(fun.y = sum, aes(label = ..y.., group = Categories), geom = "text", vjust = -.2) +
  ylim(0, 2500) +
  xlab("Decompiler") +
  ylab("# Classes") +
  facet_grid(Categories ~ .) +
  # ggtitle("Categories of Ouputs For Each Decompiler") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

ggsave(filename = "figures/recompilation_categories_results.pdf", device="pdf", height = 5, width = 8,  units = c("in"))


```

Plot the most problematic types

```{r}
# Arrange the recompilable types for which the tests fail 
tmp1 <- dataset %>%
  filter(Compiler == "javac") %>% 
  filter(isRecompilable == TRUE & passTests == FALSE) %>%
  group_by(Class) %>%
  count() %>%
  arrange(desc(n)) %>%
  filter(n > 1) %>% 
  dplyr::rename(TF = n)

tmp2 <- dataset %>%
  filter(Compiler == "javac") %>% 
  filter(isRecompilable == FALSE & passTests == FALSE) %>%
  group_by(Class) %>%
  count() %>%
  arrange(desc(n)) %>% 
  dplyr::rename(FF = n)
  
tmp3 <- dataset %>%
  filter(Compiler == "javac") %>% 
  filter(isRecompilable == TRUE & passTests == TRUE) %>%
  group_by(Class) %>%
  count() %>%
  arrange(desc(n)) %>% 
  dplyr::rename(TT = n)

problematicClasses <- dplyr::left_join(dplyr::left_join(tmp1, tmp2, by="Class"), tmp3, by = "Class") %>% 
  replace_na(list(TF = 0, FF = 0, TT = 0)) %>% 
  mutate(Metaproblem = ifelse((TF + FF) == 8, TRUE, FALSE))

table(problematicClasses$Metaproblem)

problematicClasses %>% 
  filter(Metaproblem == TRUE)

# Sort types by number of decompilers that fail
tmp1 <- tmp1[order(tmp1$TF),]
tmp1$Class <- factor(tmp1$Class, levels = tmp1$Class) 
  
tmp1 %>% ggplot(aes(Class, TF)) +
  geom_point(stat = 'identity', fill = "black", size = 2)  +
  geom_segment(aes(
    y = 0,
    x = Class,
    yend = TF,
    xend = Class
  ),
  color = "black") +
  ylab("# Decompilers that Fail Tests") +
  xlab("Classes") +
  ggtitle("Recompilable Classes for Which the Tests Fail") +
  coord_flip()

ggsave(filename = "figures/recompilable_types_fail_tests.pdf", device="pdf", height = 5, width = 8,  units = c("in"))
```

### Decompilation results for each decompiler

```{r}
breaks <- c(0, 0.25, 0.5, 0.75, 1)
tmp <- dataset %>%
  dplyr::select(Decompiler,
                Compiler,
                isDecompilable,
                isRecompilable,
                passTests) %>%
  mutate(Category = ifelse(
    isDecompilable == FALSE,
    "NOT D",
    ifelse(
      isDecompilable == TRUE & isRecompilable == FALSE,
      "D AND NOT R",
      ifelse(isDecompilable == TRUE & isRecompilable == TRUE,
             "D AND R",
             "NA")
    )
  )) %>%
  dplyr::select(Decompiler, Compiler, Category) %>%
  group_by(Decompiler, Compiler, Category) %>%
  dplyr::summarise(Count = n()) %>%
  mutate(Perc = round(Count / sum(Count) * 100, digits=1)) 

tmp$Category <- as.factor(tmp$Category)
# tmp$Category <-  relevel(tmp$Category , 'NOT D')
tmp$Category <- factor(tmp$Category, levels=c("NOT D", "D AND NOT R", "D AND R"), labels=c( "NOT Dec","Dec NOT Rec","Dec AND Rec"))

tmp %>% ggplot(aes(Compiler, Perc, label = paste0(Perc, "%"), fill = Category)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  scale_y_continuous(labels = scales::percent(breaks), label_value(NULL)) +
  scale_fill_manual(values = c("#F8766D", "#619CFF",  "#00BA38")) +
  facet_grid(Decompiler ~ .) +
  theme(legend.position="top") 

ggsave(filename = "figures/decompilation_categories_results.pdf", device="pdf", height = 6, width = 7,  units = c("in"))
```

### Ratio ratio bytecode diff=0 vs != 0

```{r}
# Ratio for all types per decompiler
dataset %>%
  na.omit() %>%
  dplyr::select(Decompiler, Project, isRecompilable, passTests, bytecodeDistance) %>%
  filter(isRecompilable ==  TRUE & passTests == TRUE) %>% 
  dplyr::select(Decompiler, bytecodeDistance) %>% 
  mutate(Diff = as.factor(ifelse(bytecodeDistance == 0, "diffEqual0", "diffNotEqual0"))) %>% 
  count(Decompiler, Diff) 

# Ratio for all decompilers
tmp1 <- dataset %>%
  na.omit() %>%
  dplyr::select(Decompiler, Project, isRecompilable, passTests, bytecodeDistance, ClassCompiler) %>%
  filter(isRecompilable ==  TRUE & passTests == TRUE)

# Classes that are recompilable and testable for all decompilers
tmp2 <- dataset %>%
  filter(isRecompilable == "TRUE" & passTests == "TRUE" & Compiler == "javac") %>% 
  select(ClassCompiler, Decompiler, passTests) %>%
  spread(Decompiler, passTests) %>%
  filter(
      `CFR` == T &
      `Dava` == T &
      `Fernflower` == T &
      `JADX` == T &
      `JD` == T &
      `Jode` == T &
      `Krakatau` == T &
      `Procyon` == T
  ) %>% 
  select(ClassCompiler)

# Ratio for the intersection (Classes that recompile and pass test for all decompilers)
inner_join(tmp1, tmp2, by="ClassCompiler") %>% 
  dplyr::select(Decompiler, bytecodeDistance) %>% 
  mutate(Diff = as.factor(ifelse(bytecodeDistance == 0, "diffEqual0", "diffNotEqual0"))) %>% 
  count(Decompiler, Diff) 

# Plot Recompile and passTests
dataset %>%
  na.omit() %>%
  dplyr::select(Decompiler, Project, isRecompilable, passTests, bytecodeDistance) %>%
  filter(isRecompilable ==  TRUE & passTests == TRUE) %>% 
  dplyr::select(Decompiler, bytecodeDistance) %>% 
  mutate(Equivalence = as.factor(ifelse(bytecodeDistance == 0, "Strict", "Modulo Input"))) %>% 
  count(Decompiler, Equivalence) %>% 
  ggplot(aes(x = reorder(Decompiler, -n), y = n, label = n, fill = Equivalence)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = c("#F8766D", "#619CFF",  "#00BA38")) +
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  ylab("# Classes") +
  xlab("Decompiler") +
  theme(legend.position="top") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

ggsave(filename = "figures/equivalence_categories_results.pdf", device="pdf", height = 4, width = 7,  units = c("in"))
```

