---
title: "Venn Diagrams"
output: html_notebook
---

This notebook plot Venn Diagrams of the results obtained with the decompilers.

# Load required packages

```{r}
library(tidyverse)
library(venn)
theme_set(theme_bw())
```

# Read the dataset

```{r}
dataset <- read.csv("data/dataset.csv")
dataset <- dataset %>% filter(Compiler == "javac")
```

# Venn Diagrams

### Venn Diagram of recompilable classes

```{r}
a <- dataset %>% 
  filter(Decompiler == "CFR" & isRecompilable == "TRUE") %>% 
  select(Class)

b <- dataset %>% 
  filter(Decompiler == "Procyon" & isRecompilable == "TRUE") %>% 
  select(Class)

c <- dataset %>% 
  filter(Decompiler == "JD" & isRecompilable == "TRUE") %>% 
  select(Class)

d <- dataset %>% 
  filter(Decompiler == "Jode" & isRecompilable == "TRUE") %>% 
  select(Class)

e <- dataset %>% 
  filter(Decompiler == "Krakatau" & isRecompilable == "TRUE") %>% 
  select(Class)

f <- dataset %>% 
  filter(Decompiler == "Fernflower" & isRecompilable == "TRUE") %>% 
  select(Class)

g <- dataset %>% 
  filter(Decompiler == "Dava" & isRecompilable == "TRUE") %>% 
  select(Class)

h <- dataset %>% 
  filter(Decompiler == "JADX" & isRecompilable == "TRUE") %>% 
  select(Class)

# decompilersToPlot <- list(a$Class, b$Class, c$Class, d$Class, e$Class, f$Class, g$Class)
# snames <- c("CFR", "Procyon",  "JD", "Jode", "Krakatau", "Fernflower", "Dava")
decompilersToPlot <- list(a$Class, b$Class, c$Class, d$Class, e$Class, f$Class, h$Class)
snames <- c("CFR", "Procyon",  "JD", "Jode", "Krakatau", "Fernflower", "JADX")
pdf("figures/venn_diagram_recompilable.pdf")
venn(
  decompilersToPlot,
  snames = snames,
  ilab = TRUE,
  zcolor = "style"
)
dev.off() 

# Types that are recompilable for each decompiler
dataset %>%
  select(Class, Compiler, Decompiler, isRecompilable) %>%
  spread(Decompiler, isRecompilable) %>%
  filter(
      `CFR` == F &
      `Dava` == F &
      `Fernflower` == F &
      `JADX` == F &
      `JD` == F &
      `Jode` == F &
      `Krakatau` == F &
      `Procyon` == F
  ) 
```

### Venn Diagram of tests that pass

```{r}
a <- dataset %>% 
  filter(Decompiler == "CFR" & passTests == "TRUE") %>% 
  select(Class)

b <- dataset %>% 
  filter(Decompiler == "Procyon" & passTests == "TRUE") %>% 
  select(Class)

c <- dataset %>% 
  filter(Decompiler == "JD" & passTests == "TRUE") %>% 
  select(Class)

d <- dataset %>% 
  filter(Decompiler == "Jode" & passTests == "TRUE") %>% 
  select(Class)

e <- dataset %>% 
  filter(Decompiler == "Krakatau" & passTests == "TRUE") %>% 
  select(Class)

f <- dataset %>% 
  filter(Decompiler == "Fernflower" & passTests == "TRUE") %>% 
  select(Class)

g <- dataset %>% 
  filter(Decompiler == "Dava" & passTests == "TRUE") %>% 
  select(Class)

h <- dataset %>% 
  filter(Decompiler == "JADX" & passTests == "TRUE") %>% 
  select(Class)

# decompilersToPlot <- list(a$Class, b$Class, c$Class, d$Class, e$Class, f$Class, g$Class)
# snames <- c("CFR", "Procyon",  "JD", "Jode", "Krakatau", "Fernflower", "Dava")
decompilersToPlot <- list(a$Class, b$Class, c$Class, d$Class, e$Class, f$Class, h$Class)
snames <- c("CFR", "Procyon",  "JD", "Jode", "Krakatau", "Fernflower", "JADX")
pdf("figures/venn_diagram_testable.pdf")
venn(
  decompilersToPlot,
  snames = snames,
  ilab = TRUE,
  zcolor = "style"
)
dev.off() 

# Types that are recompilable for each decompiler
dataset %>%
  select(Class, Compiler, Decompiler, passTests) %>%
  spread(Decompiler, passTests) %>%
  filter(
      `CFR` == T &
      `Dava` == T &
      `Fernflower` == T &
      `JADX` == T &
      `JD` == T &
      `Jode` == T &
      `Krakatau` == T &
      `Procyon` == T
  ) 
```

### Venn Digram of failures

```{r}
a <- dataset %>%
  filter(Decompiler == "CFR" & passTests == "FALSE") %>%
  select(Class)

b <- dataset %>%
  filter(Decompiler == "Procyon" & passTests == "FALSE") %>%
  select(Class)

c <- dataset %>%
  filter(Decompiler == "JD" & passTests == "FALSE") %>%
  select(Class)

d <- dataset %>%
  filter(Decompiler == "Jode" & passTests == "FALSE") %>%
  select(Class)

e <- dataset %>%
  filter(Decompiler == "Krakatau" & passTests == "FALSE") %>%
  select(Class)

f <- dataset %>%
  filter(Decompiler == "Fernflower" & passTests == "FALSE") %>%
  select(Class)

g <- dataset %>%
  filter(Decompiler == "Dava" & passTests == "FALSE") %>%
  select(Class)

h <- dataset %>% 
  filter(Decompiler == "JADX" & passTests == "FALSE") %>% 
  select(Class)

# decompilersToPlot <- list(a$Class, b$Class, c$Class, d$Class, e$Class, f$Class, g$Class)
# snames <- c("CFR", "Procyon",  "JD", "Jode", "Krakatau", "Fernflower", "Dava")
decompilersToPlot <- list(a$Class, b$Class, c$Class, d$Class, e$Class, f$Class, h$Class)
snames <- c("CFR", "Procyon",  "JD", "Jode", "Krakatau", "Fernflower", "JADX")
pdf("figures/venn_diagram_failures.pdf")
  venn(
    decompilersToPlot,
    snames = snames,
    ilab = TRUE,
    zcolor = "style"
  )
dev.off() 
```

### Venn Diagram of types which are recompilable but do not pass tests and at least one decompiler is able to make it recompilable and pass tests (i.e. how good a decompiler is decompiling types for which others fail?)

```{r}
RnotT <- dataset %>%
  filter(isRecompilable == TRUE & passTests == FALSE) %>%
  dplyr::select(Decompiler, Project, Class, passTests)

RT <- dataset %>%
  filter(isRecompilable == TRUE & passTests == TRUE) %>%
  dplyr::select(Decompiler, Project, Class, passTests)

join_dataset <- dplyr::inner_join(RnotT, RT, by = c("Class", "Project"))

# View the result of the join for better understandability 
View(join_dataset)

a <- join_dataset %>%
  filter(Decompiler.y == "CFR" & passTests.y == "TRUE") %>%
  select(Class)

b <- join_dataset %>%
  filter(Decompiler.y == "Procyon" & passTests.y == "TRUE") %>%
  select(Class)

c <- join_dataset %>%
  filter(Decompiler.y == "JD" & passTests.y == "TRUE") %>%
  select(Class)

d <- join_dataset %>%
  filter(Decompiler.y == "Jode" & passTests.y == "TRUE") %>%
  select(Class)

e <- join_dataset %>%
  filter(Decompiler.y == "Krakatau" & passTests.y == "TRUE") %>%
  select(Class)

f <- join_dataset %>%
  filter(Decompiler.y == "Fernflower" & passTests.y == "TRUE") %>%
  select(Class)

g <- join_dataset %>%
  filter(Decompiler.y == "Dava" & passTests.y == "TRUE") %>%
  select(Class)

h <- dataset %>% 
  filter(Decompiler.y == "JADX" & passTests.y == "TRUE") %>% 
  select(Class)

# decompilersToPlot <- list(a$Class, b$Class, c$Class, d$Class, e$Class, f$Class, g$Class)
# snames <- c("CFR", "Procyon",  "JD", "Jode", "Krakatau", "Fernflower", "Dava")
decompilersToPlot <- list(a$Class, b$Class, c$Class, d$Class, e$Class, f$Class, h$Class)
snames <- c("CFR", "Procyon",  "JD", "Jode", "Krakatau", "Fernflower", "JADX")
pdf("figures/venn_diagram_types_others_fail.pdf")
  venn(
    decompilersToPlot,
    snames = snames,
    ilab = TRUE,
    zcolor = "style"
  )
dev.off() 
```